embedplyr: Tools for Working With Text Embeddings

### 2025-01-08 paper/paper.Rmd
compile paper workflow

---
title: 'embedplyr: Tools for Working With Text Embeddings'
tags:
  - R
  - natural language processing
  - embeddings
  - word embeddings
  - sentiment analysis
  - psychology
authors:
  - name: Louis Teitelbaum
    orcid: 0009-0001-9347-0145
    affiliation: 1
affiliations:
  - index: 1
    name: Ben-Gurion University of the Negev, Israel
date: 10 January 2025
year: 2025
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
---

>>>>

---
title: 'embedplyr: Tools for Working With Text Embeddings'
tags:
  - R
  - natural language processing
  - embeddings
  - word embeddings
  - sentiment analysis
  - psychology
authors:
  - name: Louis Teitelbaum
    orcid: 0009-0001-9347-0145
    affiliation: 1
affiliations:
  - index: 1
    name: Ben-Gurion University of the Negev, Israel
date: 10 January 2025
year: 2025
bibliography: paper.bib
output:
  html_document:
    df_print: paged
csl: apa.csl
journal: JOSS
---
